Interaction network structure maximizes community-level plant reproduction success via niche complementarity

### 2019-06-28 paper_round2.Rmd
last changes before 1st submission to PCI

Words in main text (excluding abstract, acknowledgements, references, table and figure legends):

Number of references: 45

Number of figures, tables and text boxes:

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of plant species. However, research has focused primarily on pairwise plant-pollinator interactions, largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants. Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that, for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators. 
\nextpage

@@

  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals. Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017]. Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.

@@

  Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]). Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [@Bascompte2003] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. However, the pathways by which the structure of these networks of interactions affect key ecosystem functions such as plant reproduction remain to be understood [@Winfree2013]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

  Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community, as a measure of evenness and stability in the pollination service.

  Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient. However, we find that a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig. 1). Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period. In addition, at each round we conducted 3 minutes of focal observations on 3 individuals per species belonging to the 19 most common species across the study area (`r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site). Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were seen immediately after, as some of these interactions are difficult so see and might be important to define network structure. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days.

@@

Within each site, we marked between `r min(f.inds$tot.inds)` and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events. For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for `r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits, `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`) and average seed weight per fruit at the end of the season. Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness. Centrality represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network, where links between plant species represent shared pollinator species. As a measure of centrality we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009]. Here, links between plant species represent shared pollinator species.
  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].

@@

  Niche complementariety metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). To calculate niche complmentarity, we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a]. All network metrics were calculated using package bipartite [@Dormann2009].

@@

In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs). In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on community structure.

  At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site. The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009]. Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using a normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.

  At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled, for each species for which we used normal distributions). We thus had a single value per site and no random effects are needed in this case.

  Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized [explain how, normalizations usually make 0 centred values, and values above 0.5 makes no sense]() average fruitset values above 0.5. We repeated this using 0.25 and 0.75 thresholds. We then used the same framework as that used for species and community-level analyses and fit the same models 1 and 2 GLMs, but using equity in reproductive success as the response variable fitting a binomial distribution. In all cases, we used information criterion methods to find the best model and selected the ones with the lowest Akaike Information Criterion (AIC) value. Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011].

@@

  To test this, we ran a simple simulation in which the number of species considered increased at each time step and for each time step we re-calculated equity in reproductive success. Instead of drawing plant species randomly for each run, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g. for n = 3 plant selected out of 6 there is only 20 possible combiations). Then, we tested the overall relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) within our simulated communities. To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regressed this against our network level predictor and extracted the model estimates. We averaged all estimates from 1,000 simulated combinations per number of plants considered. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.

@@

Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators. Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera, `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera, while Araneaeae and Neuroptera representing `r round(d.order$prop[d.order$order=="Araneae"]*100, digits=2)`% each.

@@

  Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig. S1). Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a]. In addition, the fact that we include rare interactions observed outside of our main sampling, or singletons, might also be affecting our results.

@@

@@

f2$functional.comp.poll.sc<-scale(f2$functional.comp.poll, center = T, scale = T)
f2$nodf.song.sc<-scale(f2$nodf.song, center = T, scale = T)
f2$species.poll.sc<-scale(f2$species.poll, center = T, scale = T)
f2$norm_degree.sc<-scale(f2$norm_degree, center = T, scale = T)
f2$weigh_closeness.sc<-scale(f2$weigh_closeness, center = T, scale = T)
f2$niche.overlap.sc<-scale(f2$niche.overlap, center = T, scale = T)

@@

At the species level, in the case of fruitset, our results show that model 2 is the best model explaining the variability observed. In this case, we find a positive effect of a simple visitation metric, pollinator species diversity (measured using the species´normalised degree, Fig. 2) as well as a positive effect of a community structure metric, the centrality of the focal plant on its fruitset (Table 1, Fig. 2).

@@

m1<-glmer(tot.fruitset ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)

@@

m2<-glmer(tot.fruitset ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)

@@

# extract coefficients and p-values for m2 and present them in paper
coefs.m2 <- data.frame(coef(summary(m2)))
coefs.m2
Table1<-round(coefs.m2[,1:3],digits=2)
rownames(Table1)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
#at the end of the paper

#both models equally good, plot significant variables, in this case degree, do partial residual plots to show the effect of that variable in isolation of the others

@@

y_partial_norm <- remef(m2, fix= c( "tot.visits.sc", "weigh_closeness.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_norm_inv<-exp(y_partial_norm)/(1+exp(y_partial_norm))
#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs

pl1<-ggplot(m2@frame,  aes(x=m2@frame$norm_degree.sc, y=y_partial_norm_inv, color=Plant.sp)) +    
  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Normalized degree") +      
  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.35)) +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.1), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"), legend.direction = "horizontal")

#pl1

y_partial_weigh <- remef(m2, fix= c( "tot.visits.sc", "norm_degree.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_weigh_inv<-exp(y_partial_weigh)/(1+exp(y_partial_weigh))

pl1b<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Centrality") +      
  ylab(" ") + theme_bw()  + theme (legend.position= "top") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"), legend.direction = "horizontal")

#pl1b

 prow <- plot_grid( pl1 + theme(legend.position="none"),
           pl1b + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B"),
           hjust = -1,
           nrow = 1
           )

# extract the legend from one of the plots
legend_b <- get_legend(pl1 + theme(legend.position="bottom"))

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
Figure2 <- plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .2))

@@

@@

s3$norm_degree.sc<-scale(s3$norm_degree, center = T, scale = T)
s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)

@@

  For the number of seeds per fruit, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2. In this case, we find a positive effect of the niche overlap between plant species (Table 2, Fig. 3).

@@

m1.seed<-glmer(mean.seedn.sc ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)

@@

m2.seed<-glmer(mean.seedn.sc ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)

@@

AICtab(m1.seed, m2.seed) #both models are equally good.

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
# use normal distribution to approximate p-value
#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
coefs.m2.seed
Table2<-round(coefs.m2.seed,digits=2)
rownames(Table2)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")

>>>>

Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 4,451

Number of references: 48

Number of figures, tables and text boxes: 7

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of plant species. However, research has focused primarily on pairwise plant-pollinator interactions, largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants. Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved plant-pollinator networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that, for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on community structure, particularly that reflecting niche complementarity between pollinators. 
\nextpage

@@

  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals. Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013]. Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.

@@

  Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarily driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]). Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [@Bascompte2003] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. However, the pathways by which the structure of these networks of interactions affect key ecosystem functions such as plant reproduction remain to be understood [@Winfree2013]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

  Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community, as a measure of evenness in the pollination service delivered.

  Our results suggest that for prediction purposes, information on simple visitation metrics, particularly regarding the diversity of pollinators that visit a plant species, is sufficient. However, we find that a mechanistic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success requires additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species.

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig. 1). Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period. In addition, at each round we conducted 3 minutes of focal observations on 3 individuals per species belonging to the 19 most common species across the study area (`r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site). Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were opportunistically recorded immediately before or after the sampling periods, as some of these interactions are difficult to document and might be important to define network structure [@Jordano2016]. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days.

@@

Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events. For each individual, at the end of the season, we 
recorded fruit set (i.e. the proportion of flowers that set fruit), the average number of seeds per fruit and the average seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean = `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`). Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness. 
 Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016]. As a measure of centrality we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009]. Here, links between plant species represent shared pollinator species.

@@

  Niche complementarity metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). To calculate niche complementarity, we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences measured using a Euclidean distance in visitor assemblages between plants [@Devoto2012; @Petchey2007a]. All network metrics were calculated using package bipartite [@Dormann2009].

@@

In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs). In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on community structure. All response variables were previously scaled for each species to allow meaningful comparisons across species with contrasting life histories.

  At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant (i.e. pollinator richness), and the total number of visits received by that plant species; while model 2 added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site. Response variables included fruit set for different individuals of each species analyzed using a binomial distribution, the average number of seeds per fruit analyzed using a normal distribution and the average values per species of fruit and seed weight fitted to poisson distributions.

  At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator richness and total pollinator abundance (i.e., the number of visits received by all plants within the community) as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution). All metrics were previously scaled for each species to allow meaningful comparisons across species with contrasting life histories. We thus had a single value per site and no random effects are needed in this case.

  Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized (between 0 and 1) average fruit set values that were above 0.5. We repeated this using 0.25 and 0.75 thresholds. We then used the same framework as that used for species and community-level analyses and fit the same models 1 and 2 GLMs, but using equity in reproductive success as the response variable fitting a binomial distribution. In all cases, we used information criterion methods to find the best model and selected the ones with the lowest Akaike Information Criterion (AIC) value. Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011]. All predictor variables were centered prior to analysis.

@@

  To test this, we ran a simple simulation in which the number of species considered increased at each step and for each step we re-calculated equity in reproductive success. Instead of drawing plant species randomly for each step, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g. for n = 3 plant selected out of 6 there is only 20 possible combinations). Then, we tested if the relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities. To this end, for each level of species number considered, we randomly selected one of the generated equity values across each of the 16 communities, and regressed these 16 values against our network level predictor and extracted the model estimates. We repeated this process 1,000 times and averaged all estimates. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species considered depends on the initial number of combinations.

@@

Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators. Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera and `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera.

@@

  Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average = 35%), 47-98% for plant species (average = 78%) and 13-41% for plant-pollinator links (average = 27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig. S1). Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a]. In addition, the fact that we include an extra effort to capture rare interactions observed outside of our main sampling might also increase the number of singletons which directly affect richness estimates.

@@

#calculate number of pollinator species per plant species instead of norm_degree

sites <- unique(d$Site_ID)
plants<-unique(d$Plant_gen_sp)

out <- data.frame(Site_id = NA, plant.sps = NA, poll.sps = NA)

for(i in 1:length(sites)){
  temp <- subset(d, Site_ID == sites[i])
  for(j in 1:length(plants)){
      temp2 <- subset(temp, Plant_gen_sp == plants[j])
  temp3<-droplevels(temp2)

  poll<-nlevels(unique(temp3$Pollinator_gen_sp))

  n <- nrow(out)

  out[n + 1,1] <- as.character(sites[i])
  out[n + 1,2] <- as.character(plants[j])
  out[n + 1,3] <- poll

}
}
out

out2<-out[-1,]
out2$match<-paste(out2$Site_id, out2$plant.sps)

f2$pollspsperplant<-out2$poll.sps[match(f2$match, out2$match)]

@@

f2$functional.comp.poll.sc<-scale(f2$functional.comp.poll, center = T, scale = T)
f2$nodf.song.sc<-scale(f2$nodf.song, center = T, scale = T)
f2$species.poll.sc<-scale(f2$species.poll, center = T, scale = T)
f2$norm_degree.sc<-scale(f2$norm_degree, center = T, scale = T)
f2$weigh_closeness.sc<-scale(f2$weigh_closeness, center = T, scale = T)
f2$niche.overlap.sc<-scale(f2$niche.overlap, center = T, scale = T)
f2$pollspsperplant.sc<-scale(f2$pollspsperplant, center = T, scale = T)

@@

At the species level, in the case of fruitset, our results show that model 2 is the best model explaining the variability observed. In this case, we find a positive effect of a simple visitation metric, pollinator species diversity (measured using the species´normalised degree, Fig. 2) as well as a positive effect of a community structure metric, the centrality of the focal plant on its fruit set (Table 1A, Fig. 2A).

@@

m1<-glmer(tot.fruitset ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)

@@

m2<-glmer(tot.fruitset ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)

@@

# extract coefficients and p-values for m2 and present them in paper
coefs.m2 <- data.frame(coef(summary(m2)))
coefs.m2
Table1A<-round(coefs.m2[,1:3],digits=2)
rownames(Table1A)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
#at the end of the paper

#both models equally good, plot significant variables, in this case centrality, do partial residual plots to show the effect of that variable in isolation of the others

@@

y_partial_weigh <- remef(m2, fix= c( "tot.visits.sc", "pollspsperplant.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_weigh_inv<-exp(y_partial_weigh)/(1+exp(y_partial_weigh))

Figure2a<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc, y=y_partial_weigh_inv, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Centrality") +      
  ylab("Fruit set ") + theme_bw()  + theme (legend.position= "bottom") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"), legend.direction = "horizontal")

#Figure2a

@@

s3$pollspsperplant<-out2$poll.sps[match(s3$match, out2$match)]

@@

s3$norm_degree.sc<-scale(s3$norm_degree, center = T, scale = T)
s3$weigh_closeness.sc<-scale(s3$weigh_closeness, center = T, scale = T)
s3$niche.overlap.sc<-scale(s3$niche.overlap, center = T, scale = T)
s3$pollspsperplant.sc<-scale(s3$pollspsperplant, center = T, scale = T)

@@

 For the number of seeds per fruit, our results show again that model 2 is the best model. In this case, we find a positive effect of the niche overlap between plant species (Table 1B, Fig. 2B).

@@

m1.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)

@@

m2.seed<-glmer(mean.seedn.sc ~  pollspsperplant.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s4_scaled)

@@

AICtab(m1.seed, m2.seed) #m2 is best

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
# use normal distribution to approximate p-value
#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
coefs.m2.seed
Table1B<-round(coefs.m2.seed,digits=2)
rownames(Table1B)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
